---
title: "musica.tools: tools to extract and plot MuSICA outputs"
output: github_document
---


```{r echo=FALSE, message=FALSE, results="hide"}
options(Encoding = "UTF-8")
library(badger)
```


<!-- `r badger::badge_cran_release("segclust2d", "orange")` -->
<!-- `r badger::badge_cran_download("segclust2d", "grand-total", "yellow")` -->
`r badger::badge_github_version("rpatin/musica.tools", "blue")`
`r badger::badge_last_commit("rpatin/musica.tools")`

# Introduction

`musica.tools` provides several function to extract MuSICA output from netcdf files. 
Output can then be used to produce a series of generic plots.

# Website

Full documentation for musica.tools will soon be available on this website:
[https://rpatin.github.io/musica.tools/](https://rpatin.github.io/musica.tools/)

# Installation

<!-- For the `r badger::badge_cran_release("segclust2d", "orange")` version  :  -->
<!-- ```{r, eval=FALSE} -->
<!-- install.packages("segclust2d") -->
<!-- ``` -->

If you want the newest `r badger::badge_devel("rpatin/musica.tools", "blue")`, you
can install `musica.tools` from github  with:

```{r, eval=FALSE}
devtools::install_github("rpatin/musica.tools")
```